---
title: "Multiple Linear Regression Model Analysis"
author: "T.W. MANHEMA"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

#Introduction

#Aim: The aim is to analyze the relationship between the percentage calories obtained from complex carbohydrates and the explanatory variables using appropriate models.

## 1.Data Collection

Data was collected

### Loading the data

Loaded the data from a csv file

### Converting the data into a data frame

Converted the data into a data frame so we can easily work with it.

```{r setup,'include = FALSE',`echo = TRUE`}
knitr::opts_chunk$set(include = FALSE)
#Transform the data into a data frame
carbohydratesData <- data.frame(carbohydratesData)
```

## 2.Exploratory Data Analysis

viewing the structure of the data and seeing the kind of variables to work with.

```{r setup, include = TRUE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
head(carbohydratesData)
```

### Examining the data

### Cleaning the data by removing missing values

Cleaning the data by removing any missing values

```{r setup, include=TRUE, echo= FALSE}
knitr::opts_chunk$set(eval = FALSE, include = FALSE)
clean_data <- na.omit(carbohydratesData)
```

### Generating Summary Statistics of the data

```{r setup, include=TRUE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
summary(clean_data)
```

## 3.Model Fitting

After examining of the data, the response variables and explanatory variables are discovered and will be used to fit a multiple linear regression model.

###Fitting a multiple linear regression model with the data Below is the code and formula of the model we are fitting.

```{r setup, include=FALSE, echo=TRUE}
carb_mlr <- lm(calories_obtained~ weight + protein + age, data = clean_data)

```

## 4.Getting Summary of the model

After fitting the model, we extract a summary of it, for further analysis.

### Model summary:

```{r setup, include=TRUE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
summary(carb_mlr)

```

## Interpretation of Coeficients:

-   Intercept: The estimated percentage of total calorie intake, when all other variables are zero is 36.96%

-   Weight: For every 1-unit increase of weight, there is an estimated 0.23% decrease in total calorie intake.

-   Protein: For every 1-unit increase in protein, there is an estimated 1.96% increase in total calorie intake.

-   Age: For every 1-unit increase in age, there is an estimated 0.11% decrease in total calorie intake.

#### Significance of the coefficients to the model

-   The Weight coefficient has a p-value of 0.01, thus suggesting that it is significant to the model.

-   The Protein coefficient has a p-value of 0.007, thus suggesting that it is highly significant to the model fitted.

-   The age coefficient has a large p-value of 0.31, suggesting that it may not be significant to our model.

### Overral Model Significance

We examine the R-squared and F-statistic to come with conclusions about the adequeccy of the model.

-   R-squared: According to this, approximately 48% of the variability of the total percentage of the carollies obtained from complex carbohydrates is explained by predictor variables. This suggests that the overall model fit is good.

-   F-statistic: The value is 4.934 with a p-value of 0.013.This suggests that the overall model is statistically significant.

# 5.Checking if Model Assumptions are met

The following are the assumptions of a linear regression model:

##### a.Linearity

##### b.Homoscedascity

##### c.Normality

##### d.Independence
